Weighted Model Counting with Conditional Weights for Bayesian Networks

### 2020-12-16 doc/paper1/paper.tex
Initial setup for a new BN preprocessor (and moving some files around)

\newpage
\appendix
\section{Proofs}

@@

>>>>

\newpage
\appendix
\section{Technical Appendix}

\subsection{Proofs}

@@

\subsection{Reproducibility Checklist}

Here we provide the rationale behind some of our answers to the questions in the
reproducibility checklist.
\begin{itemize}
%\item The authors are not aware of any significant limitations or technical
%  assumptions worth mentioning.
\item The proof of Theorem~2 is not explicitly included as the idea behind the
  proof is illustrated via an example.
\item While we provide citations for papers that describe and/or introduce most
  of the Bayesian networks used in our experiments, some of the classical
  Bayesian networks used in the experiments are widely used and never cited.
  Their origin can sometimes be traced to groups of people but not specific
  papers.
\item For our evaluation metrics, we count numbers of instances that were
  solved using each encoding, numbers of instances where each encoding
  outperformed others (including situations when multiple runs of the algorithm
  result in exactly the same amount of time), and numbers of instances that are
  solved by using only one encoding. As these metrics are quite elementary and
  secondary to the cumulative and scatter plots, we do not describe the
  motivation for using them.
\item None of the plots or metrics in the paper have any measure of error
  associated with them. For Figure~2 and Table~2, this is because each curve or
  number is interpreted as a statistic of a single experiment. Figure~3, on the
  other hand, provides a visual summary of every single experimental run.
\end{itemize}
